Towards a robust desicion tool for ecosystems services in the industrial systems: A case study of Distributed recycling for additive manufacturing

### 2021-10-22 00-ES/PubliER/PubliER.Rmd
dibujo conceptual

---
title: "Towards a robust desicion tool for ecosystems services in the industrial systems:  A case study of Distributed recycling for additive manufacturing"
#documentclass: extarticle
#fontsize: 14pt
#geometry: "left=2cm, right=2cm,top=3cm,bottom=2cm"
output: 
  bookdown::pdf_document2:
    toc: true
    keep_tex: TRUE
    #pandoc_args: "--latex-engine-opt=--shell-escape"
  # bookdown::html_document2: default
  # bookdown::word_document2: default
#output: rticles::tf_article
# abstract
always_allow_html: true
# editor_options: 
#   markdown: 
#     wrap: 100
bibliography: library.bib
#bibliography: References.bib
link-citations: yes
linkcolor: blue
header-includes: |
  \usepackage{float}
  \usepackage{subfig}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \usepackage[bitstream-charter]{mathdesign}
  \usepackage{pdflscape}
  \usepackage{svg}
  \usepackage{lineno}
  \usepackage{setspace}
  \newcommand*{\doverline}[1]{\overline{\overline{#1}}}
  \usepackage{tabu}

@@

# img_url <- paste0(URL, 'Everest-bio/Methodology.svg')
# rsvg_pdf(img_url, "Figures/Methodology.pdf")

@@

<!-- Distributed Fabrication -->
Major technological advance in the Additive manufacturing field have enable the validation of distributed fabrication

In the same logic, recently, the concept of distributed recycling via additive manufacturing (DRAM) emerged in the literature to face the socio-environmental challenges related to recycling option for AM technologies using plastic material as feedstock [@CruzSanchez2020; @Santander2020]. 
The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community. 
To do so, the use of additive manufacturing enables the technical paths to achieve this objective. 
While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches. 
However, as with any recycling system, its feasibility and real impact must be evaluated before its implementation. 
<!-- Based on the sustainability concept, this research intends to investigate, how the ecosystem services are impacted due to the implementation of the plastic recycling chain.  -->
Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.

>>>>

title: "Towards a robust desicion tool for ecosystems services in the industrial systems:  A case study of Distributed recycling for additive manufacturing"
#documentclass: extarticle
#fontsize: 14pt
#geometry: "left=2cm, right=2cm,top=3cm,bottom=2cm"
output: 
  bookdown::pdf_document2:
    toc: true
    keep_tex: TRUE
    #pandoc_args: "--latex-engine-opt=--shell-escape"
  # bookdown::html_document2: default
  # bookdown::word_document2: default
#output: rticles::tf_article
abstract: |
    <!-- Intro -->
    Ecosystem services (ES) is a powerful conceptual framework to put in evidence the benefits that humans received from nature, most of time for free.
    <!-- Problem -->
    The problem is that it is complex to link between the local ecosystem services of an urban territory and the industrial systems placed within it identifying the priority interactions (as synergy and impacts).
    From a decision-maker perspective, there is no a aid decision tool to guide a multicriteria evaluation at early development stages of industrial systems.
    <!-- Conceptual Framework (broad theoretical) -->
       <!-- ES valuation and Urban  ES-->
    There have been major efforts in the valuation of ES given by ecosystems (terrestrial, aquatic, atmospheric) to the human well-being [@Costanza2017; @DeGroot2012; @MEA2005; @Costanza1997], and  great advances in the developing of a standard ES baselines such as Common International Classification of Ecosystem Services (CICES)[@RoyHaines-Young2018]. 
    <!-- Knowledge Gap -->
    However, few researches have been addressed the alignment the territorial priorities in terms of ES for planning and urban development with the supply/demand of ES by industrial systems.
    <!-- Logic & Evidence for Problem, KG and Context -->
       <!-- LCA -->
    In the industrial side, Life cycle thinking have been a major assessment tool putting a great attention in the quantification of the environmental impact of industrial interventions, and helping in the comparison of different scenarios in each aspect stage of the product life [@Mahmud2021; @Pryshlakivsky2021]. 
       <!-- LCA AND ES -->
    Recently, several research efforts reported  accounts for the dependence systems by explicitly accounting for the demand that technological systems place on ecosystems and the supply of ecosystem services that nature can provide to a process or product at multiple spatial scales [@Liu2019g].
    This techno-ecological synergy (TES) [@Liu2019g; @Bakshi2015] to reflect its emphasis on establishing mutually beneficial or synergistic relationships between technological and ecological systems, with the ultimate goal of achieving harmony between human activities and nature.
    <!-- Purpose Statement -->
    The purpose of this article is to propose a methodological approach in order to include ecosystem services in regarding the territorial and industrial endeavors.
       <!-- Expand a methodology -->
    This prioritization is based on the connection of urban ES services and the techno-ecological synergy.
    The results of are step forwards to create techno-ecological synergies between ecological and industrial systems.
    <!-- Context -->
    This methodological steps will applied to the case of distributed recycling via additive manufacturing (DRAM) to highlight the relevant ES from the CICES framework of this industrial system for the territory of Nancy, France. 
    The technical advancements of recycling approaches using additive manufacturing are promising technical interventions to foster plastic recycling at a local level.
always_allow_html: true
# editor_options: 
#   markdown: 
#     wrap: 100
bibliography: library.bib
#bibliography: References.bib
link-citations: yes
linkcolor: blue
header-includes: |
  \usepackage{float}
  \usepackage{subfig}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \usepackage[bitstream-charter]{mathdesign}
  \usepackage{pdflscape}
  \usepackage{svg}
  \usepackage{lineno}
  \usepackage{setspace}
  \newcommand*{\doverline}[1]{\overline{\overline{#1}}}
  \usepackage{tabu}

@@

# img_url <- paste0(URL, 'Everest-bio/Publier/Methodology.svg')
# rsvg_pdf(img_url, "Figures/Methodology.pdf")

@@

<!-- Distributed Fabrication -->
Major technological advance in the Additive manufacturing field have enable the validation of distributed fabrication.
In the same logic, recently, the concept of distributed recycling via additive manufacturing (DRAM) emerged in the literature to face the socio-environmental challenges related to recycling option for AM technologies using plastic material as feedstock [@CruzSanchez2020; @Santander2020].

The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community. 
To do so, the use of additive manufacturing enables the technical paths to achieve this objective. 
While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches. 
However, as with any recycling system, its feasibility and real impact must be evaluated before its implementation. 
<!-- Based on the sustainability concept, this research intends to investigate, how the ecosystem services are impacted due to the implementation of the plastic recycling chain.  -->
Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.

### 2021-10-22 00-ES/PubliER/PubliER.tex
dibujo conceptual

\begin{document}
\maketitle

@@

Major technological advance in the Additive manufacturing field have enable the validation of distributed fabrication

In the same logic, recently, the concept of distributed recycling via additive manufacturing (DRAM) emerged in the literature to face the socio-environmental challenges related to recycling option for AM technologies using plastic material as feedstock (\protect\hyperlink{ref-CruzSanchez2020}{Cruz Sanchez et al. 2020}; \protect\hyperlink{ref-Santander2020}{Santander et al. 2020}).
The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community.
To do so, the use of additive manufacturing enables the technical paths to achieve this objective.
While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches.
However, as with any recycling system, its feasibility and real impact must be evaluated before its implementation.
Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.

@@

@@

@@

@@

>>>>

\begin{document}
\maketitle
\begin{abstract}
Ecosystem services (ES) is a powerful conceptual framework to put in evidence the benefits that humans received from nature, most of time for free.
The problem is that it is complex to link between the local ecosystem services of an urban territory and the industrial systems placed within it identifying the priority interactions (as synergy and impacts).
From a decision-maker perspective, there is no a aid decision tool to guide a multicriteria evaluation at early development stages of industrial systems.
There have been major efforts in the valuation of ES given by ecosystems (terrestrial, aquatic, atmospheric) to the human well-being (\protect\hyperlink{ref-Costanza2017}{Costanza et al. 2017}, \protect\hyperlink{ref-Costanza1997}{1997}; \protect\hyperlink{ref-DeGroot2012}{Groot et al. 2012}; \protect\hyperlink{ref-MEA2005}{MEA 2005}), and great advances in the developing of a standard ES baselines such as Common International Classification of Ecosystem Services (CICES)(\protect\hyperlink{ref-RoyHaines-Young2018}{Roy Haines-Young and Potschin 2018}).
However, few researches have been addressed the alignment the territorial priorities in terms of ES for planning and urban development with the supply/demand of ES by industrial systems.
In the industrial side, Life cycle thinking have been a major assessment tool putting a great attention in the quantification of the environmental impact of industrial interventions, and helping in the comparison of different scenarios in each aspect stage of the product life (\protect\hyperlink{ref-Mahmud2021}{Mahmud et al. 2021}; \protect\hyperlink{ref-Pryshlakivsky2021}{Pryshlakivsky and Searcy 2021}).
Recently, several research efforts reported accounts for the dependence systems by explicitly accounting for the demand that technological systems place on ecosystems and the supply of ecosystem services that nature can provide to a process or product at multiple spatial scales (\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi 2019}).
This techno-ecological synergy (TES) (\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi 2019}; \protect\hyperlink{ref-Bakshi2015}{Bakshi, Ziv, and Lepech 2015}) to reflect its emphasis on establishing mutually beneficial or synergistic relationships between technological and ecological systems, with the ultimate goal of achieving harmony between human activities and nature.
The purpose of this article is to propose a methodological approach in order to include ecosystem services in regarding the territorial and industrial endeavors.
This prioritization is based on the connection of urban ES services and the techno-ecological synergy.
The results of are step forwards to create techno-ecological synergies between ecological and industrial systems.
This methodological steps will applied to the case of distributed recycling via additive manufacturing (DRAM) to highlight the relevant ES from the CICES framework of this industrial system for the territory of Nancy, France.
The technical advancements of recycling approaches using additive manufacturing are promising technical interventions to foster plastic recycling at a local level.
\end{abstract}

@@

Major technological advance in the Additive manufacturing field have enable the validation of distributed fabrication.
In the same logic, recently, the concept of distributed recycling via additive manufacturing (DRAM) emerged in the literature to face the socio-environmental challenges related to recycling option for AM technologies using plastic material as feedstock (\protect\hyperlink{ref-CruzSanchez2020}{Cruz Sanchez et al. 2020}; \protect\hyperlink{ref-Santander2020}{Santander et al. 2020}).

The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community.
To do so, the use of additive manufacturing enables the technical paths to achieve this objective.
While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches.
However, as with any recycling system, its feasibility and real impact must be evaluated before its implementation.
Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.

@@

\leavevmode\hypertarget{ref-DeGroot2012}{}%
Groot, Rudolf de, Luke Brander, Sander van der Ploeg, Robert Costanza, Florence Bernard, Leon Braat, Mike Christie, et al. 2012. {``{Global estimates of the value of ecosystems and their services in monetary units}.''} \emph{Ecosyst. Serv.} 1 (1): 50--61. \url{https://doi.org/10.1016/j.ecoser.2012.07.005}.

@@

\leavevmode\hypertarget{ref-Mahmud2021}{}%
Mahmud, Roksana, Sheikh Moniruzzaman Moni, Karen High, and Michael Carbajales-Dale. 2021. {``{Integration of techno-economic analysis and life cycle assessment for sustainable process design -- A review}.''} Elsevier. \url{https://doi.org/10.1016/j.jclepro.2021.128247}.

@@

\leavevmode\hypertarget{ref-Pryshlakivsky2021}{}%
Pryshlakivsky, Jonathan, and Cory Searcy. 2021. {``{Life Cycle Assessment as a decision-making tool: Practitioner and managerial considerations}.''} Elsevier. \url{https://doi.org/10.1016/j.jclepro.2021.127344}.

@@

\leavevmode\hypertarget{ref-RoyHaines-Young2018}{}%
Roy Haines-Young, by, and Marion Potschin. 2018. {``{Common International Classification of Ecosystem Services (CICES) V5.1 Guidance on the Application of the Revised Structure}.''} \href{https://www.cices.eu}{www.cices.eu}.
